```{r}
library(tidyverse) # general data wrangling
library(patchwork) # plot composition
library(R2jags) # modelling
library(gganimate) # animating plots
```

# Barsel news analysis

## Run the model for barsel news
```{r}
# Load the data
sentences <- read_csv("data/Sentiment Analysis/Analysis Ready/barsel_sentence_data.csv")
article <- read_csv("data/Sentiment Analysis/Analysis Ready/barsel_article_data.csv")
# How many articles for each group
group_table <- article %>%
    unique() %>%
    group_by(gender,politics) %>%
    summarise(ng=n())

# Structure the data to pass it on to JAGS
data_list <- list(
    y = sentences,
    Na = max(article$Na),
    A = article$Na,
    G = unique(select(article, c(Na, group)))$group,
    ng = unique(select(left_join(article, group_table), c(Na, ng)))$ng,
    alpha = rep(1, 3) # prior
)

# Define parameters of interest
params = c("Ea", "Eg", "delta_pol", "delta_gen")
# Run the model
samples.base <- jags.parallel(data_list, inits=NULL, params, model.file ="model/Dirichlet all the way down.bugs",
                n.chains=12, n.iter=10000, n.burnin=2500, n.thin=1)# summary
# Show results
samples.base
```

## Represent the relsults: Check group and difference estimates
```{r}
# Save the results of the model
s <- tibble(data.frame(as.matrix(as.mcmc(samples.base))))

## Extract expected value for each group (1=leftmen, 2=rightmen, 3=leftwomen, 4=rightwomen)
eg <-s  %>%
    select(contains("Eg")) %>%
    pivot_longer(contains("Eg")) %>%
    separate(name, into=c("variable", "group", "sentiment")) %>%
    mutate(gender = ifelse(group %in% c(1,2), "male journalist", "female journalist"),
            politics = ifelse(group %in% c(1,3), "left-oriented", "right-oriented"))
# Plot them
eg %>%
    mutate(sentiment=case_when(sentiment == 1 ~ "positive",
                                sentiment == 2 ~ "neutral",
                                sentiment == 3 ~ "negative")) %>%
    ggplot(aes(sentiment, value, fill=politics)) +
    geom_violin(alpha=.3) + 
    geom_violin(alpha=.8) +
    facet_grid(politics~gender) +
    scale_fill_manual(name="Politics", values=c("firebrick3", "blue")) +
    theme_bw() + ylim(0, 1) + 
    ggtitle("A.") -> eg_barsel
eg_barsel

# Extract delta values
deltas <- s  %>%
    select(contains("delta")) %>%
    pivot_longer(cols=contains("delta")) %>%
    separate(name, c("variable","type", "sent")) %>%
    mutate(sentiment = case_when(sent == 1 ~ "positive",
                                    sent == 2 ~ "neutral",
                                    sent == 3 ~ "negative")
    )  %>%
    mutate(type = ifelse(type == "gen", "gender difference", "political difference")) %>%
    select(type, sentiment, value)
## delta plotting
deltas  %>%
    ggplot() +
    geom_density(aes(value, color= sentiment),size=1.2) +
    geom_vline(xintercept=0, color="red")+
    facet_grid(vars(rows=type)) +
    xlim(-.2, .2) + theme_bw() +
    scale_color_viridis_d(begin=.1,end=.9)

## Plotting with priors
# Prior on individual groups
priors_eg1 <- LaplacesDemon::rdirichlet(100000, c(1, 1, 1))
priors_eg2 <- LaplacesDemon::rdirichlet(100000, c(1, 1, 1))
priors_eg3 <- LaplacesDemon::rdirichlet(100000, c(1, 1, 1))
priors_eg4 <- LaplacesDemon::rdirichlet(100000, c(1, 1, 1))
# Prior on joint probabilities
priors_p1 <- (priors_eg1 + priors_eg2)/(rowSums(priors_eg1) + rowSums(priors_eg2))
priors_p2 <- (priors_eg3 + priors_eg4)/(rowSums(priors_eg3) + rowSums(priors_eg4))
# Prior on difference
priors <- priors_p1 - priors_p2
priors <- tibble(positive=priors[,1], neutral=priors[,2], negative=priors[,3])  %>%
                    pivot_longer(everything(), names_to = "sentiment")
# Plot posterior difference with prior difference
ggplot() +
    geom_vline(xintercept = 0, color="#666666", linetype=3) +
    geom_density(data=priors, aes(value), color="red",size=1, linetype=2, alpha=.9) +
    geom_density(data=deltas, aes(value, color= sentiment)) +
    facet_grid(.~type) +
    theme_bw() + xlim(-.6,.6) +
    scale_color_viridis_d(begin=.1,end=.9) +
    ggtitle("A.") -> delta_barsel
delta_barsel
```

## Visualise the data as a triangle
```{r}

mutate(sentences, index=row_number()) %>%
    left_join(mutate(article, index=row_number())) %>%
    ggplot(aes(negative_prob, positive_prob)) +
    geom_point(aes(color=neutral_prob), size=.4) +
    geom_density2d_filled(alpha=.3) +
    facet_grid(politics~gender) +
    scale_color_distiller(palette=14, direction=1) +
    theme_minimal()

# some animation at the article level to visualise diversity
#mutate(sentences, index=row_number()) %>%
#    left_join(mutate(article, index=row_number())) %>%
#    ggplot(aes(negative_prob, positive_prob)) +
#    geom_point(aes(color=neutral_prob)) +
#    scale_color_distiller(palette=14, direction=1) +
#    theme_minimal() +
#     transition_states(
#    Na,
#    transition_length = 5,
#    state_length = 3
#  ) +
#  enter_fade() + 
#  exit_shrink() +
#  ease_aes('sine-in-out')
#
#anim_save("bob.gif", animation = last_animation())
```

## Sampling from the posterior
```{r}
post_article <-
    tibble(
            Na = rep(seq(1,118),3),
            sent = rep(c("positive", "neutral", "negative"), each=118),
            # /!\ only using the mean of individual articles estimates
            mean = samples.base$BUGSoutput$summary[1:(118*3)],
    ) %>%
    group_by(Na) %>%
    pivot_wider(names_from = sent, values_from = mean) %>%
    # add gender info
    left_join(article %>%
        group_by(Na) %>%
        summarise(n=n(), gender, politics)) %>% 
    unique()

# generate the sentences
sim <- tibble(Na=c(NA), X1=c(NA), X2=c(NA), X3=c(NA))
for (a in post_article$Na)
{
    sim <- sim %>%
        bind_rows(
            data.frame(
                Na=a,
                gender=post_article$gender[a],
                politics=post_article$politics[a],
                LaplacesDemon::rdirichlet(post_article$n[a], c(post_article$positive[a], post_article$neutral[a], post_article$negative[a]))
                )
            )
}
sim <- filter(sim, !is.na(Na))
# plot
sim %>%
    ggplot(aes(X3, X1)) +
    geom_point(aes(color=X2), alpha=.9, size=.3) +
    geom_density2d_filled(alpha=.3) +
    facet_grid(politics~gender) +
    scale_color_distiller(palette=14, direction=1) +
    theme_minimal()
```


# Control analysis

# Run the dirichlet all the way down model on control data
```{r}
# Load the data
sentences_control <- read_csv("data/Sentiment Analysis/Analysis Ready/control_sentence_data.csv")
article_control <- read_csv("data/Sentiment Analysis/Analysis Ready/control_article_data.csv")
# How many articles for each group
group_table_control <- article_control %>%
    unique() %>%
    group_by(gender, politics) %>%
    summarise(ng=n())

# data list
data_list <- list(
    y = sentences_control,
    Na = max(article_control$Na),
    A = article_control$Na,
    G = unique(select(article_control, c(Na, group)))$group,
    ng = unique(select(left_join(article_control, group_table_control), c(Na, ng)))$ng,
    alpha = rep(1, 3) # prior
)

## Parameters of interest
params = c("Ea", "Eg", "delta_pol", "delta_gen")
# Run
samples.control <- jags.parallel(data_list, inits=NULL, params, model.file ="model/Dirichlet all the way down.bugs",
                n.chains=12, n.iter=10000, n.burnin=2500, n.thin=1)# summary
# show summary results
samples.control
```

# Represent the relsults of control analysis: Check group and difference estimates
```{r}
# Save the results
s <- tibble(data.frame(as.matrix(as.mcmc(samples.control))))

## Expected value for each group (1=leftmen, 2=rightmen, 3=leftwomen, 4=rightwomen)
eg <-s  %>%
    select(contains("Eg")) %>%
    pivot_longer(contains("Eg")) %>%
    separate(name, into=c("variable", "group", "sentiment")) %>%
    mutate(gender = ifelse(group %in% c(1,2), "man", "woman"),
            politics = ifelse(group %in% c(1,3), "left", "right"))
# Plot
eg %>%
    mutate(sentiment=case_when(sentiment == 1 ~ "positive",
                                sentiment == 2 ~ "neutral",
                                sentiment == 3 ~ "negative")) %>%
    ggplot(aes(sentiment, value, fill=politics)) +
    geom_violin(alpha=.3) + 
    geom_violin(alpha=.8) +
    facet_grid(politics~gender) +
    scale_fill_manual(name="Politics", values=c("firebrick3", "blue")) +
    theme_bw() +
    ylim(0, 1)

# extract delta parameters
deltas <- s  %>%
    select(contains("delta")) %>%
    pivot_longer(cols=contains("delta")) %>%
    separate(name, c("variable","type", "sent")) %>%
    mutate(sentiment = case_when(sent == 1 ~ "positive",
                                    sent == 2 ~ "neutral",
                                    sent == 3 ~ "negative")
    )  %>%
    mutate(type = ifelse(type == "gen", "gender difference", "political difference")) %>%
    select(type, sentiment, value)

## Plotting with priors
# Prior on individual groups
priors_eg1 <- LaplacesDemon::rdirichlet(100000, c(1, 1, 1))
priors_eg2 <- LaplacesDemon::rdirichlet(100000, c(1, 1, 1))
priors_eg3 <- LaplacesDemon::rdirichlet(100000, c(1, 1, 1))
priors_eg4 <- LaplacesDemon::rdirichlet(100000, c(1, 1, 1))
# Prior on joint probabilities
priors_p1 <- (priors_eg1 + priors_eg2)/(rowSums(priors_eg1) + rowSums(priors_eg2))
priors_p2 <- (priors_eg3 + priors_eg4)/(rowSums(priors_eg3) + rowSums(priors_eg4))
# Prior on difference
priors <- priors_p1 - priors_p2
priors <- tibble(positive=priors[,1], neutral=priors[,2], negative=priors[,3])  %>%
                    pivot_longer(everything(), names_to = "sentiment")
# Plot posterior difference with prior difference
ggplot() +
    geom_density(data=priors, aes(value), color="red",size=1, linetype=2, alpha=.9) +
    geom_density(data=deltas, aes(value, color= sentiment)) +
    facet_grid(vars(rows=type)) +
    theme_bw() + xlim(-.6,.6) +
    scale_color_viridis_d(begin=.1,end=.9)
```


# Test a difference between Barsel and Control
```{r}
# Load the data
sentences_all <- read_csv("data/Sentiment Analysis/Analysis Ready/comparaison_sentence_data.csv")
article_all <-   read_csv("data/Sentiment Analysis/Analysis Ready/comparaison_article_data.csv")
# How many articles for each group
group_table_all <- article_all %>%
    unique() %>%
    group_by(group) %>%
    summarise(ng=n())

# Format for the model
data_list <- list(
    y = sentences_all,
    Na = max(article_all$Na),
    A = article_all$Na,
    G = unique(select(article_all, c(Na, group)))$group,
    ng = unique(select(left_join(article_all, group_table_all), c(Na, ng)))$ng,
    alpha = rep(1, 3) # prior
)

## Parameters choice
params = c("Ea", "Eg", "delta_control")
# Run
samples.all <- jags.parallel(data_list, inits=NULL, params, model.file ="model/Compare with control.bugs",
                n.chains=12, n.iter=10000, n.burnin=2500, n.thin=1)
# summary
samples.all


```
## Plot the results
```{r}
# Save the results
s <- tibble(data.frame(as.matrix(as.mcmc(samples.all))))

## Expected value for each group (1=leftmen, 2=rightmen, 3=leftwomen, 4=rightwomen)
eg <-s  %>%
    select(contains("Eg")) %>%
    pivot_longer(contains("Eg")) %>%
    separate(name, into=c("variable", "group", "sentiment")) %>%
    mutate(group = ifelse(group == 1, "leave reform news", "general news"))
# Plot
eg %>%
    mutate(sentiment=case_when(sentiment == 1 ~ "positive",
                                sentiment == 2 ~ "neutral",
                                sentiment == 3 ~ "negative")) %>%
    ggplot(aes(sentiment, value, fill=group)) +
    geom_violin(alpha=.8) +
    #facet_wrap(~group) +
    scale_fill_manual(name="Group", values=c("#d0becf", "#000000")) +
    theme_bw() + ylim(0, 1) +
    ggtitle("B.") -> eg_control
eg_control

# extract delta parameters
deltas <- s  %>%
    select(contains("delta")) %>%
    pivot_longer(cols=contains("delta")) %>%
    separate(name, c("variable","type", "sent")) %>%
    mutate(sentiment = case_when(sent == 1 ~ "positive",
                                    sent == 2 ~ "neutral",
                                    sent == 3 ~ "negative")
    ) %>%
    select(type, sentiment, value)

## Plotting with priors
# Prior on individual groups
priors_eg1 <- LaplacesDemon::rdirichlet(100000, c(1, 1, 1))
priors_eg2 <- LaplacesDemon::rdirichlet(100000, c(1, 1, 1))
priors_eg3 <- LaplacesDemon::rdirichlet(100000, c(1, 1, 1))
priors_eg4 <- LaplacesDemon::rdirichlet(100000, c(1, 1, 1))
# Prior on joint probabilities
priors_p1 <- (priors_eg1 + priors_eg2)/(rowSums(priors_eg1) + rowSums(priors_eg2))
priors_p2 <- (priors_eg3 + priors_eg4)/(rowSums(priors_eg3) + rowSums(priors_eg4))
# Prior on difference
priors <- priors_p1 - priors_p2
priors <- tibble(positive=priors[,1], neutral=priors[,2], negative=priors[,3])  %>%
                    pivot_longer(everything(), names_to = "sentiment")
# Plot posterior difference with prior difference
ggplot() +
    geom_vline(xintercept = 0, color="#666666", linetype=3) +
    geom_density(data=priors, aes(value), color="red",size=1, linetype=2, alpha=.9) +
    geom_density(data=deltas, aes(value, color= sentiment)) +
    theme_bw() + xlim(-.6, .6) +
    scale_color_viridis_d(begin=.1, end=.9) +
    ggtitle("B.")-> delta_control
delta_control
```


## Compose patched up plots for the article
```{r}
# Expected values estimates
layout <- "
AAA##
AAABB
AAABB
AAABB
AAABB
AAABB
AAABB
AAABB
AAABB
AAABB
AAA##
"
eg_barsel + eg_control +
    plot_layout(design=layout)

# differences
layout <- "
AAAAAAAAAAAA
AAAAAAAAAAAA
AAAAAAAAAAAA
AAAAAAAAAAAA
AAAAAAAAAAAA
#BBBBBBBBBB#
#BBBBBBBBBB#
#BBBBBBBBBB#
#BBBBBBBBBB#
#BBBBBBBBBB#"
delta_barsel / delta_control +
    plot_layout(design=layout)
```